---
title: "case_study"
output: github_document
date: "2024-10-08"
---

```{r setup}
library(tidyverse)
library(p8105.datasets)

data(nyc_airbnb)
```
## brainstorming questions

* where are max and min air bnb prices
  * what are average prices
  * what factors affect prices
* where are prices going up and down over time?
* what's the relationship between number of reviews and average review?
* does room type affect availability?
* what's the location of the unit?
  * what areas are popular?
  * popularity = number of units? average price?
* are there repeated hosts?
  * if so, what does that mean?
```{r}
str(nyc_airbnb)
```
```{r}
max(pull(nyc_airbnb, price))
min(pull(nyc_airbnb, price))
```
```{r}
summary(nyc_airbnb)
```
```{r}
# what's the relationship between number of reviews and average review?
nyc_airbnb %>% 
  group_by(review_scores_location) %>% 
  summarize(avg_review_number = mean(number_of_reviews)) %>% 
  ggplot(aes(x = review_scores_location, y = avg_review_number, fill = review_scores_location))+
  geom_bar(stat = "identity")
  
```
```{r}
#Average price by roomtype (visualised)
nyc_airbnb %>%
  group_by(room_type) %>%
  summarise(mean_price = mean(price, na.rm = TRUE)) %>% 
  ggplot(aes(x = room_type, y = mean_price))+
  geom_bar(stat = "identity")
```

